What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Filled in missing stats

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        &&&\\
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       &&&\\
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

        40,100,000 & claiming that & 39\% &\\
        30,600,000 & the belief that & &\\
        28,600,000 & believing that & &\\
        11,700,000 & who believe that &&\\
        8,400,000 & who think that &&\\
        \hline
	&&&\\
        \multicolumn{2}{|l}{\it Something false} & &\\
	    & & &\\

@@

  \caption{Some of the patterns we use to find disputed claims}
  \label{templates-fig}
\end{figure}

>>>>

\begin{figure}[tb]
\begin{center}
  \vspace{0.5cm}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        &&&\\
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       &&&\\
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

        40,100,000 & claiming that & 39\% & 65\%\\
        11,700,000 & who believe that & 69\% & 73\%\\
        8,400,000 & who think that & 49\% & 66\%\\
        \hline
	&&&\\
        \multicolumn{2}{|l}{\it Something false} & &\\
	    & & &\\

@@

  \caption{Some of the patterns we use to find disputed claims}
  \label{templates-fig}
  \vspace{0.5cm}
\end{figure}
